### 2025-02-17 README.Rmd
modified pkgdown config

# SampleSizePlanner <a href='https://marton-balazs-kovacs.github.io/SampleSizePlanner/'><img src='man/figures/ssp_logo.png' align="right" height="200" /></a>

>>>>

# SampleSizePlanner <a href='https://marton-balazs-kovacs.github.io/SampleSizePlanner/'><img src='man/figures/ssp_logo.png' align="right" height="200" alt-text="SampleSizePlanner"/></a>
